Approximation as Differentiation

### 2025-05-05 appendix/notes/auto-diff.tex
cartesian -> Cartesian.
Start on Galois slicing.

>>>>

\subsubsection{Galois slicing via category of families}

Now recall that the category $\Fam(\LatGal)$ is the Grothendieck construction $\Grothendieck{X}\Fam(X,
\LatGal)$, with:
\begin{itemize}
\item as objects $(X, \partial X)$ all pairs of a set $X$ and and for each $x \in X$, a bounded lattice
$\partial X_x$;
\item as morphisms $(X, \partial X) \to (Y, \partial Y)$, all pairs $(f, \partial f)$ of functions $f: X \to
Y$ and Galois connections $\partial f: \partial X_x \to \partial Y_{f(x)}$.
\end{itemize}
